---
title: "Empathy and perspective taking"
subtitle: "Analyses"
author: "Ian Hussey"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

# TODO

- add distribution plots for all (sub)scales
- not all subscales in TRT plots
- add internal consistency subscales
- add bar plot for IC
- add second set of correlations for t2? could put in supplementaries
- could include the PTTA and PTT analyses very briefly as exploratory, ie just to replicate the weird claim that spatial and emotional PT are correlated (no) and that the PTT measures PT (well, doesn't correlate with other PT tasks).

# Overview

All included measures are used as measures of empathy or to make conclusions about empathy. While some may be used to examine different facets of empathy, this distinction is a) not theoretically agreed upon, as there is little consensus around the structure of empathy, and therefore b) not necessarily reflected in their measurement (i.e., low correlations may represent poor convergent validity rather than good discriminant validity).

This study examines a) the reliability of these scales (internal consistency, test-retest reliability) relative to the original published estimates, and b) the risk of jingle fallacy (via correlations among [sub]scales).  

NB EQ subscales based on Lawrence et al., 2004.

```{r, include=FALSE}
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)
```

# Dependencies

```{r}

library(readr)
library(dplyr)
library(tidyr)
library(stringr)
library(forcats)
library(irr)
library(psych)
library(lavaan)
library(janitor)
library(ggplot2)
library(patchwork)
library(ggstance)
library(ggrain)
library(scales)
library(mirt)
library(correlation)
library(see)
library(insight)
library(purrr)
library(knitr)
library(kableExtra)

options(scipen=999)

dir.create("plots")

```

# Load data

```{r}

data_processed <- read_csv("../data/processed/data_processed.csv") |>
  select(-starts_with("PTP_") & -starts_with("PTTA_"))

data_processed_after_exclusions <- data_processed |>
  filter(exclude_master == "include")

```

# Demographics

## Sample sizes and exclusions

```{r}

data_processed |>
  count(timepoint, exclude_master) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

```

## Analytic sample (timepoint 1)

```{r}

data_processed_after_exclusions |>
  filter(timepoint == 1) |>
  count(gender) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

data_processed_after_exclusions |>
  filter(timepoint == 1) |>
  dplyr::summarize(mean_age = mean(age),
                   sd_age = sd(age),
                   min_age = min(age),
                   max_age = max(age)) |>
  pivot_longer(cols = everything()) |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

data_processed_after_exclusions |>
  distinct(unique_id, .keep_all = TRUE) |>
  ggplot(aes(age)) +
  geom_histogram(binwidth = 5) +
  theme_linedraw()

```

# Analyses

## Test-retest

$ICC_{2,1}$

### Results

```{r}

data_reshaped <- data_processed_after_exclusions |>
  select(unique_id, timepoint, SITES, IRI_FS, IRI_EC, IRI_PT, IRI_PD, IRI_total, EQ_total, EQ_cog, EQ_aff, EQ_soc, PET_total, EYES_total) |>
  pivot_wider(id_cols = unique_id,
              names_from = timepoint,
              values_from = c(SITES, IRI_FS, IRI_EC, IRI_PT, IRI_PD, IRI_total, EQ_total, EQ_cog, EQ_aff, EQ_soc, PET_total, EYES_total))

tidy_icc_2_1 <- function(data, scale){
  res <- data |>
    select(starts_with(scale)) |>
    irr::icc(model = "twoway", type = "agreement", unit = "single",
             r0 = 0, conf.level = 0.95)
  
  tibble(scale = scale,
         icc_2.1 = res$value,
         ci_lower = res$lbound,
         ci_upper = res$ubound)
}

res <- bind_rows(
  tidy_icc_2_1(data_reshaped, "SITES"),
  tidy_icc_2_1(data_reshaped, "IRI_FS"),
  tidy_icc_2_1(data_reshaped, "IRI_EC"),
  tidy_icc_2_1(data_reshaped, "IRI_PT"),
  tidy_icc_2_1(data_reshaped, "IRI_PD"),
  tidy_icc_2_1(data_reshaped, "IRI_total"),
  tidy_icc_2_1(data_reshaped, "EQ_total"),
  tidy_icc_2_1(data_reshaped, "EQ_cog"),
  tidy_icc_2_1(data_reshaped, "EQ_aff"),
  tidy_icc_2_1(data_reshaped, "EQ_soc"),
  tidy_icc_2_1(data_reshaped, "PET_total"),
  tidy_icc_2_1(data_reshaped, "EYES_total")
)
  
res |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

```

### Plots

#### Bar

```{r fig.height=5, fig.width=6}

p_trt_scales <- res |>
  filter(str_detect(scale, "SITES") | str_detect(scale, "_total")) |>
  mutate(scale = str_remove(scale, "_total")) |>
  ggplot(aes(icc_2.1, fct_rev(scale))) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  geom_linerangeh(aes(xmin = ci_lower, xmax = ci_upper), position = position_dodge(width = .3)) +
  geom_point(position = position_dodge(width = .3)) +
  scale_x_continuous(breaks = breaks_pretty(n = 10),
                     limits = c(-.2, 1),
                     name = bquote(ICC["2,1"])) +
  theme_linedraw() +
  ylab("Scale")

p_trt_subscales <- res |>
  filter(!str_detect(scale, "_total") & !str_detect(scale, "SITES")) |>
  mutate(scale = str_replace(scale, "_", " ")) |>
  mutate(scale = str_replace(scale, "doublereversed", "double")) |>
  ggplot(aes(icc_2.1, fct_rev(scale))) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  geom_linerangeh(aes(xmin = ci_lower, xmax = ci_upper), position = position_dodge(width = .3)) +
  geom_point(position = position_dodge(width = .3)) +
  scale_x_continuous(breaks = breaks_pretty(n = 10),
                     limits = c(-.2, 1),
                     name = bquote(ICC["2,1"])) +
  theme_linedraw() +
  ylab("Subscale")

p_trt_scales + 
  p_trt_subscales + 
  plot_layout(ncol = 1, heights = c(1, 1.35))

ggsave("plots/trt.png", 
       width = 6,
       height = 5,
       dpi = 600)

```

#### Raincloud

```{r fig.height=14, fig.width=12}

round_half_up_trailing <- function(x, digits = 2) {
  x_rounded <- round_half_up(x, digits = digits)
  sprintf("%.*f", digits, x_rounded)
}

res_print <- res |>
  mutate(across(where(is.numeric), ~ round_half_up_trailing(.x, digits = 2))) |>
  mutate(string = paste0("= ", icc_2.1, ", 95% CI [", ci_lower, ", ", ci_upper, "]")) |>
  select(scale, string)

data_reshaped_plotting <- data_processed_after_exclusions |>
  select(unique_id, timepoint, SITES, IRI_FS, IRI_EC, IRI_PT, IRI_PD, IRI_total, EQ_total, EQ_cog, EQ_aff, EQ_soc, PET_total, EYES_total) |>
  pivot_longer(cols = c(SITES, IRI_FS, IRI_EC, IRI_PT, IRI_PD, IRI_total, EQ_total, EQ_cog, EQ_aff, EQ_soc, PET_total, EYES_total),
               names_to = "scale",
               values_to = "score")

p_trt_1 <- data_reshaped_plotting |>
  filter(scale == "IRI_total") |>
  ggplot(aes(as.factor(timepoint), score, fill = as.factor(timepoint))) +
  geom_rain(alpha = .5, rain.side = 'f1x1', id.long.var = "unique_id") +
  theme_classic() +
  scale_fill_manual(values=c("dodgerblue", "darkorange")) +
  guides(fill = 'none', color = 'none') +
  ylab("Score") +
  xlab("Time point") +
  ggtitle(bquote("Interpersonal Reactivity Index:" ~ ICC["2,1"] ~ .(res_print |> filter(scale == "IRI_total") |> pull(string)))) +
  scale_y_continuous(breaks = scales::breaks_pretty(n = 6))

p_trt_2 <- data_reshaped_plotting |>
  filter(scale == "IRI_PT") |>
  ggplot(aes(as.factor(timepoint), score, fill = as.factor(timepoint))) +
  geom_rain(alpha = .5, rain.side = 'f1x1', id.long.var = "unique_id") +
  theme_classic() +
  scale_fill_manual(values=c("dodgerblue", "darkorange")) +
  guides(fill = 'none', color = 'none') +
  ylab("Score") +
  xlab("Time point") +
  ggtitle(bquote("IRI - Perspective Taking Subscale:" ~ ICC["2,1"] ~ .(res_print |> filter(scale == "IRI_PT") |> pull(string)))) +
  scale_y_continuous(breaks = scales::breaks_pretty(n = 6))

p_trt_3 <- data_reshaped_plotting |>
  filter(scale == "SITES") |>
  ggplot(aes(as.factor(timepoint), score, fill = as.factor(timepoint))) +
  geom_rain(alpha = .5, rain.side = 'f1x1', id.long.var = "unique_id", likert = TRUE) +
  theme_classic() +
  scale_fill_manual(values=c("dodgerblue", "darkorange")) +
  guides(fill = 'none', color = 'none') +
  ylab("Score") +
  xlab("Time point") +
  ggtitle(bquote("Single Item Trait Empathy Scale:" ~ ICC["2,1"] ~ .(res_print |> filter(scale == "SITES") |> pull(string)))) +
  scale_y_continuous(breaks = scales::breaks_pretty(n = 6))

p_trt_4 <- data_reshaped_plotting |>
  filter(scale == "PET_total") |>
  ggplot(aes(as.factor(timepoint), score, fill = as.factor(timepoint))) +
  geom_rain(alpha = .5, rain.side = 'f1x1', id.long.var = "unique_id") +
  theme_classic() +
  scale_fill_manual(values=c("dodgerblue", "darkorange")) +
  guides(fill = 'none', color = 'none') +
  ylab("Score") +
  xlab("Time point") +
  ggtitle(bquote("Pictoral Empathy Test:" ~ ICC["2,1"] ~ .(res_print |> filter(scale == "PET_total") |> pull(string)))) +
  scale_y_continuous(breaks = scales::breaks_pretty(n = 6))

p_trt_5 <- data_reshaped_plotting |>
  filter(scale == "EQ_total") |>
  ggplot(aes(as.factor(timepoint), score, fill = as.factor(timepoint))) +
  geom_rain(alpha = .5, rain.side = 'f1x1', id.long.var = "unique_id") +
  theme_classic() +
  scale_fill_manual(values=c("dodgerblue", "darkorange")) +
  guides(fill = 'none', color = 'none') +
  ylab("Score") +
  xlab("Time point") +
  ggtitle(bquote("Emotional Quotient:" ~ ICC["2,1"] ~ .(res_print |> filter(scale == "EQ_total") |> pull(string)))) +
  scale_y_continuous(breaks = scales::breaks_pretty(n = 6))

p_trt_6 <- data_reshaped_plotting |>
  filter(scale == "EYES_total") |>
  ggplot(aes(as.factor(timepoint), score, fill = as.factor(timepoint))) +
  geom_rain(alpha = .5, rain.side = 'f1x1', id.long.var = "unique_id") +
  theme_classic() +
  scale_fill_manual(values=c("dodgerblue", "darkorange")) +
  guides(fill = 'none', color = 'none') +
  ylab("Score") +
  xlab("Time point") +
  ggtitle(bquote("Reading the Mind in the Eyes Test:" ~ ICC["2,1"] ~ .(res_print |> filter(scale == "EYES_total") |> pull(string)))) +
  scale_y_continuous(breaks = scales::breaks_pretty(n = 6))

p_trt_1 + p_trt_2 + p_trt_3 + p_trt_4 +
  p_trt_5 + p_trt_6 + 
  plot_layout(ncol = 2)

```

## Internal consistency 

Cronbach's $\alpha$

```{r}

data_subset <- data_processed_after_exclusions |>
  dplyr::select(timepoint, 
                starts_with("IRI_"), 
                starts_with("EQ_"),
                starts_with("PET_"),
                starts_with("EYES_")) |>
  dplyr::select(-IRI_FS, -IRI_EC, -IRI_PT, -IRI_PD, -EQ_cog, -EQ_aff, -EQ_soc) |>
  dplyr::select(!ends_with("_completeness") & !ends_with("_total"))

tidy_alpha <- function(data, time, scale){
  res <- data |>
    filter(timepoint == time) |>
    dplyr::select(starts_with(scale)) |>
    psych::alpha()
  
  res2 <- res$feldt 
  
  tibble(scale = scale,
         timepoint = time,
         alpha = res2$alpha$raw_alpha,
         ci_lower = res2$lower.ci$raw_alpha,
         ci_upper = res2$upper.ci$raw_alpha)
}

res <- bind_rows(
  tidy_alpha(data = data_subset, time = 1, scale = "IRI_"),
  #tidy_alpha(data = data_subset, time = 2, scale = "IRI_"),
  tidy_alpha(data = data_subset, time = 1, scale = "EQ_"),
  #tidy_alpha(data = data_subset, time = 2, scale = "EQ_"),
  tidy_alpha(data = data_subset, time = 1, scale = "PET_"),
  #tidy_alpha(data = data_subset, time = 2, scale = "PET_"),
  tidy_alpha(data = data_subset, time = 1, scale = "EYES_"),
  #tidy_alpha(data = data_subset, time = 2, scale = "EYES_")
)

res |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

```

## Correlations

### T1

```{r}

dat <- data_processed |>
  filter(timepoint == 1)

```

#### Scale correlations

```{r fig.height=4.5}

scale_cors <- dat |>
  select(SITES, ends_with("_total")) |>
  rename_with(~ str_remove(.x, "_total")) %>%
  select(order(colnames(.))) |>
  correlation()

res <- scale_cors |>
  as.data.frame() |>
  select(Parameter1, Parameter2, r, ci_low = CI_low, ci_high = CI_high, p) 

res |>
  mutate(p = insight::format_p(p)) |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

p1_t1 <- 
  ggplot(res, aes(r)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_histogram(binwidth = 0.1, boundary = 0) +
  scale_x_continuous(limits = c(-1, 1), 
                     name = "Correlation", 
                     breaks = scales::breaks_pretty(n = 10)) + 
  scale_y_continuous(name = "Frequency", 
                     breaks = scales::breaks_pretty(n = 7)) + 
  theme_linedraw() +
  theme(panel.grid.minor.y = element_blank())

#p1
  
p2_t1 <- 
  scale_cors |>
  summary(redundant = TRUE) |>
  plot(show_data = "points",
       stars = FALSE) +
  theme_linedraw() +
  ggtitle("")

#p2 + coord_fixed(ratio = 1)

# scale_cors |>
#   summary() |>
#   plot(show_data = "points",
#        stars = FALSE) +
#   theme_linedraw() +
#   ggtitle("") +
#   coord_fixed(ratio = 1)

average_cors_all <- res |>
  dplyr::summarize(mean_r = mean(r),
                   sd_r = sd(r),
                   median_r = median(r),
                   mad_r = mad(r),
                   min_r = min(r),
                   max_r = max(r)) 

average_cors_all |>
  round_half_up(digits = 2) |>
  kable() |>
  kable_classic(full_width = FALSE)

```

```{r fig.height=7, fig.width=6}

p1_t1 + ggtitle("Correlation histogram") +
  p2_t1 + ggtitle("Correlation matrix") + 
  plot_layout(ncol = 1, heights = c(.4, 1))

ggsave("plots/cor_scales_t1.png", 
       width = 6,
       height = 7,
       dpi = 600)

```

#### Subscale correlations

```{r fig.height=6, fig.width=11}

subscale_cors <- dat |>
  select(SITES, 
         IRI_FS, IRI_EC, IRI_PT, IRI_PD, 
         EQ_cog, EQ_aff, EQ_soc, 
         PET_total,
         EYES_total) |>
  rename_with(~ str_remove(.x, "_total")) |>
  correlation() 

subscale_cors |>
  as.data.frame() |>
  select(Parameter1, Parameter2, r, ci_low = CI_low, ci_high = CI_high, p) |>
  mutate(p = insight::format_p(p)) |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

p3_t1 <- 
  ggplot(subscale_cors, aes(r)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_histogram(binwidth = 0.1, boundary = 0) +
  scale_x_continuous(limits = c(-1, 1), 
                     name = "Correlation", 
                     breaks = scales::breaks_pretty(n = 10)) + 
  scale_y_continuous(name = "Frequency", 
                     breaks = scales::breaks_pretty(n = 7)) + 
  theme_linedraw() +
  theme(panel.grid.minor.y = element_blank())

#p3_t1

# code repeated in order to use the rename, which screws up the table but is needed for the plot
p4_t1 <- dat |>
  select(SITES, 
         IRI_FS, IRI_EC, IRI_PT, IRI_PD, 
         EQ_cog, EQ_aff, EQ_soc, 
         PET_total,
         EYES_total) |>
  rename_with(~ str_remove(.x, "_total")) |>
  rename_with(~ str_replace(.x, "_", "\n")) %>%
  select(order(colnames(.))) |>
  correlation() %>%
  mutate(across(where(is.numeric), ~ round_half_up(., 2))) |>
  summary(redundant = TRUE) |>
  plot(show_data = "points",
       stars = FALSE) +
  theme_linedraw() +
  ggtitle("")

#p4_t1

```

```{r fig.height=9, fig.width=7}

p3_t1 + ggtitle("Correlation histogram") +
  p4_t1 + ggtitle("Correlation matrix") + 
  plot_layout(ncol = 1, heights = c(.4, 1))

ggsave("plots/cor_subscales_t1.png", 
       width = 7,
       height = 9,
       dpi = 600)

```

### T2

```{r}

dat <- data_processed |>
  filter(timepoint == 2)

```

#### Scale correlations

```{r fig.height=4.5}

scale_cors <- dat |>
  select(SITES, ends_with("_total")) |>
  rename_with(~ str_remove(.x, "_total")) %>%
  select(order(colnames(.))) |>
  correlation()

res <- scale_cors |>
  as.data.frame() |>
  select(Parameter1, Parameter2, r, ci_low = CI_low, ci_high = CI_high, p) 

res |>
  mutate(p = insight::format_p(p)) |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

p1_t2 <- 
  ggplot(res, aes(r)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_histogram(binwidth = 0.1, boundary = 0) +
  scale_x_continuous(limits = c(-1, 1), 
                     name = "Correlation", 
                     breaks = scales::breaks_pretty(n = 10)) + 
  scale_y_continuous(name = "Frequency", 
                     breaks = scales::breaks_pretty(n = 7)) + 
  theme_linedraw() +
  theme(panel.grid.minor.y = element_blank())

#p1_t2
  
p2_t2 <- 
  scale_cors |>
  summary(redundant = TRUE) |>
  plot(show_data = "points",
       stars = FALSE) +
  theme_linedraw() +
  ggtitle("")

#p2_t2 + coord_fixed(ratio = 1)

# scale_cors |>
#   summary() |>
#   plot(show_data = "points",
#        stars = FALSE) +
#   theme_linedraw() +
#   ggtitle("") +
#   coord_fixed(ratio = 1)

average_cors_all <- res |>
  dplyr::summarize(mean_r = mean(r),
                   sd_r = sd(r),
                   median_r = median(r),
                   mad_r = mad(r),
                   min_r = min(r),
                   max_r = max(r)) 

average_cors_all |>
  round_half_up(digits = 2) |>
  kable() |>
  kable_classic(full_width = FALSE)

```

```{r fig.height=7, fig.width=6}

p1_t2 + ggtitle("Correlation histogram") +
  p2_t2 + ggtitle("Correlation matrix") + 
  plot_layout(ncol = 1, heights = c(.4, 1))

ggsave("plots/cor_scales_t2.png", 
       width = 6,
       height = 7,
       dpi = 600)

```

#### Subscale correlations

```{r fig.height=6, fig.width=11}

subscale_cors <- dat |>
  select(SITES, 
         IRI_FS, IRI_EC, IRI_PT, IRI_PD, 
         EQ_cog, EQ_aff, EQ_soc, 
         PET_total,
         EYES_total) |>
  rename_with(~ str_remove(.x, "_total")) |>
  correlation() 

subscale_cors |>
  as.data.frame() |>
  select(Parameter1, Parameter2, r, ci_low = CI_low, ci_high = CI_high, p) |>
  mutate(p = insight::format_p(p)) |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

p3_t2 <- 
  ggplot(subscale_cors, aes(r)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_histogram(binwidth = 0.1, boundary = 0) +
  scale_x_continuous(limits = c(-1, 1), 
                     name = "Correlation", 
                     breaks = scales::breaks_pretty(n = 10)) + 
  scale_y_continuous(name = "Frequency", 
                     breaks = scales::breaks_pretty(n = 7)) + 
  theme_linedraw() +
  theme(panel.grid.minor.y = element_blank())

#p3_t2

# code repeated in order to use the rename, which screws up the table but is needed for the plot
p4_t2 <- dat |>
  select(SITES, 
         IRI_FS, IRI_EC, IRI_PT, IRI_PD, 
         EQ_cog, EQ_aff, EQ_soc, 
         PET_total,
         EYES_total) |>
  rename_with(~ str_remove(.x, "_total")) |>
  rename_with(~ str_replace(.x, "_", "\n")) %>%
  select(order(colnames(.))) |>
  correlation() %>%
  mutate(across(where(is.numeric), ~ round_half_up(., 2))) |>
  summary(redundant = TRUE) |>
  plot(show_data = "points",
       stars = FALSE) +
  theme_linedraw() +
  ggtitle("")

#p4_t2

```

```{r fig.height=9, fig.width=7}

p3_t2 + ggtitle("Correlation histogram") +
  p4_t2 + ggtitle("Correlation matrix") + 
  plot_layout(ncol = 1, heights = c(.4, 1))

ggsave("plots/cor_subscales_t2.png", 
       width = 7,
       height = 9,
       dpi = 600)

```

### Both times - scales

```{r fig.height=6, fig.width=9.35}

p1_t1 + ggtitle("Correlation histogram (T1)") +
  p1_t2 + ggtitle("Correlation matrix (T2)") + 
  p2_t1 + ggtitle("Correlation histogram (T1)") +
  p2_t2 + ggtitle("Correlation matrix (T2)") + 
  plot_layout(ncol = 2, heights = c(.4, 1), guides = "collect")

ggsave("plots/cor_scales_both.png", 
       width = 9.35,
       height = 6,
       dpi = 600)

```

### Both times - subscales

```{r fig.height=9, fig.width=13.2}

p3_t1 + ggtitle("Correlation histogram (T1)") +
  p3_t2 + ggtitle("Correlation matrix (T2)") + 
  p4_t1 + ggtitle("Correlation histogram (T1)") +
  p4_t2 + ggtitle("Correlation matrix (T2)") + 
  plot_layout(ncol = 2, heights = c(.4, 1), guides = "collect")

ggsave("plots/cor_subscales_both.png", 
       width = 13.2,
       height = 9,
       dpi = 600)

```


# Session info

```{r}

sessionInfo()

```



