---
title: "Empathy and perspective taking"
subtitle: "Analyses"
author: "Ian Hussey"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

Reworking of Marcus' code

# Overview

- A shortened version of the PT protocol is shown to have very bad internal consistency, test-retest reliability, convergent validity, and poor structural validity.
- The issue is that it is a shortened version of the protocol. For this to be more widely accepted, we might need to run an additional study with a longer version of it. 

# TODO

- remove PTTA from CFA? it was a separate exploratory hypothesis

```{r, include=FALSE}
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)
```

# Dependencies

```{r}

library(readr)
library(dplyr)
library(tidyr)
library(stringr)
library(forcats)
library(irr)
library(psych)
library(lavaan)
library(janitor)
library(ggplot2)
library(ggrain)
library(scales)
library(mirt)
library(correlation)
library(see)
library(insight)
library(purrr)
library(knitr)
library(kableExtra)

options(scipen=999)

```

# Load data

```{r}

data_processed <- read_csv("../data/processed/data_processed.csv") 

data_processed_after_exclusions <- data_processed |>
  filter(exclude_master == "include")

```

# Demographics

## Sample sizes and exclusions

```{r}

data_processed |>
  count(timepoint, exclude_master) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

```

## Analytic sample (timepoint 1)

```{r}

data_processed_after_exclusions |>
  filter(timepoint == 1) |>
  count(gender) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

data_processed_after_exclusions |>
  filter(timepoint == 1) |>
  dplyr::summarize(mean_age = mean(age),
                   sd_age = sd(age),
                   min_age = min(age),
                   max_age = max(age)) |>
  pivot_longer(cols = everything()) |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

data_processed_after_exclusions |>
  distinct(unique_id, .keep_all = TRUE) |>
  ggplot(aes(age)) +
  geom_histogram(binwidth = 5) +
  theme_linedraw()

```

# Analyses

## Test-retest

$ICC_{2,1}$

### Results

```{r}

data_reshaped <- data_processed_after_exclusions |>
  select(unique_id, timepoint, SITES, IRI_FS, IRI_EC, IRI_PT, IRI_PD, IRI_total, EQ_total, PET_total, EYES_total, PTP_simple, PTP_reversed, PTP_doublereversed, PTP_total, PTTA_total) |>
  pivot_wider(id_cols = unique_id,
              names_from = timepoint,
              values_from = c(SITES, IRI_FS, IRI_EC, IRI_PT, IRI_PD, IRI_total, EQ_total, PET_total, EYES_total, PTP_simple, PTP_reversed, PTP_doublereversed, PTP_total, PTTA_total))

tidy_icc_2_1 <- function(data, scale){
  res <- data |>
    select(starts_with(scale)) |>
    irr::icc(model = "twoway", type = "agreement", unit = "single",
             r0 = 0, conf.level = 0.95)
  
  tibble(scale = scale,
         icc_2.1 = res$value,
         ci_lower = res$lbound,
         ci_upper = res$ubound)
}

res <- bind_rows(
  tidy_icc_2_1(data_reshaped, "SITES"),
  tidy_icc_2_1(data_reshaped, "IRI_FS"),
  tidy_icc_2_1(data_reshaped, "IRI_EC"),
  tidy_icc_2_1(data_reshaped, "IRI_PT"),
  tidy_icc_2_1(data_reshaped, "IRI_PD"),
  tidy_icc_2_1(data_reshaped, "IRI_total"),
  tidy_icc_2_1(data_reshaped, "EQ_total"),
  tidy_icc_2_1(data_reshaped, "PET_total"),
  tidy_icc_2_1(data_reshaped, "EYES_total"),
  tidy_icc_2_1(data_reshaped, "PTP_simple"),
  tidy_icc_2_1(data_reshaped, "PTP_reversed"),
  tidy_icc_2_1(data_reshaped, "PTP_doublereversed"),
  tidy_icc_2_1(data_reshaped, "PTP_total"),
  tidy_icc_2_1(data_reshaped, "PTTA_total")
)
  
res |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

```

### Plots

```{r}

round_half_up_trailing <- function(x, digits = 2) {
  x_rounded <- round_half_up(x, digits = digits)
  sprintf("%.*f", digits, x_rounded)
}

res_print <- res |>
  mutate(across(where(is.numeric), ~ round_half_up_trailing(.x, digits = 2))) |>
  mutate(string = paste0("= ", icc_2.1, ", 95% CI [", ci_lower, ", ", ci_upper, "]")) |>
  select(scale, string)

data_reshaped_plotting <- data_processed_after_exclusions |>
  select(unique_id, timepoint, SITES, IRI_FS, IRI_EC, IRI_PT, IRI_PD, IRI_total, EQ_total, PET_total, EYES_total, PTP_total, PTTA_total) |>
  pivot_longer(cols = c(SITES, IRI_FS, IRI_EC, IRI_PT, IRI_PD, IRI_total, EQ_total, PET_total, EYES_total, PTP_total, PTTA_total),
               names_to = "scale",
               values_to = "score")

data_reshaped_plotting |>
  filter(scale == "IRI_total") |>
  ggplot(aes(as.factor(timepoint), score, fill = as.factor(timepoint))) +
  geom_rain(alpha = .5, rain.side = 'f1x1', id.long.var = "unique_id") +
  theme_classic() +
  scale_fill_manual(values=c("dodgerblue", "darkorange")) +
  guides(fill = 'none', color = 'none') +
  ylab("Score") +
  xlab("Time point") +
  ggtitle(bquote("Interpersonal Reactivity Index:" ~ ICC["2,1"] ~ .(res_print |> filter(scale == "IRI_total") |> pull(string)))) +
  scale_y_continuous(breaks = scales::breaks_pretty(n = 6))

data_reshaped_plotting |>
  filter(scale == "IRI_PT") |>
  ggplot(aes(as.factor(timepoint), score, fill = as.factor(timepoint))) +
  geom_rain(alpha = .5, rain.side = 'f1x1', id.long.var = "unique_id") +
  theme_classic() +
  scale_fill_manual(values=c("dodgerblue", "darkorange")) +
  guides(fill = 'none', color = 'none') +
  ylab("Score") +
  xlab("Time point") +
  ggtitle(bquote("IRI - Perspective Taking Subscale:" ~ ICC["2,1"] ~ .(res_print |> filter(scale == "IRI_PT") |> pull(string)))) +
  scale_y_continuous(breaks = scales::breaks_pretty(n = 6))

data_reshaped_plotting |>
  filter(scale == "SITES") |>
  ggplot(aes(as.factor(timepoint), score, fill = as.factor(timepoint))) +
  geom_rain(alpha = .5, rain.side = 'f1x1', id.long.var = "unique_id", likert = TRUE) +
  theme_classic() +
  scale_fill_manual(values=c("dodgerblue", "darkorange")) +
  guides(fill = 'none', color = 'none') +
  ylab("Score") +
  xlab("Time point") +
  ggtitle(bquote("Single Item Trait Empathy Scale:" ~ ICC["2,1"] ~ .(res_print |> filter(scale == "SITES") |> pull(string)))) +
  scale_y_continuous(breaks = scales::breaks_pretty(n = 6))

data_reshaped_plotting |>
  filter(scale == "PET_total") |>
  ggplot(aes(as.factor(timepoint), score, fill = as.factor(timepoint))) +
  geom_rain(alpha = .5, rain.side = 'f1x1', id.long.var = "unique_id") +
  theme_classic() +
  scale_fill_manual(values=c("dodgerblue", "darkorange")) +
  guides(fill = 'none', color = 'none') +
  ylab("Score") +
  xlab("Time point") +
  ggtitle(bquote("Pictoral Empathy Test:" ~ ICC["2,1"] ~ .(res_print |> filter(scale == "PET_total") |> pull(string)))) +
  scale_y_continuous(breaks = scales::breaks_pretty(n = 6))

data_reshaped_plotting |>
  filter(scale == "EQ_total") |>
  ggplot(aes(as.factor(timepoint), score, fill = as.factor(timepoint))) +
  geom_rain(alpha = .5, rain.side = 'f1x1', id.long.var = "unique_id") +
  theme_classic() +
  scale_fill_manual(values=c("dodgerblue", "darkorange")) +
  guides(fill = 'none', color = 'none') +
  ylab("Score") +
  xlab("Time point") +
  ggtitle(bquote("Emotional Quotient:" ~ ICC["2,1"] ~ .(res_print |> filter(scale == "EQ_total") |> pull(string)))) +
  scale_y_continuous(breaks = scales::breaks_pretty(n = 6))

data_reshaped_plotting |>
  filter(scale == "EYES_total") |>
  ggplot(aes(as.factor(timepoint), score, fill = as.factor(timepoint))) +
  geom_rain(alpha = .5, rain.side = 'f1x1', id.long.var = "unique_id") +
  theme_classic() +
  scale_fill_manual(values=c("dodgerblue", "darkorange")) +
  guides(fill = 'none', color = 'none') +
  ylab("Score") +
  xlab("Time point") +
  ggtitle(bquote("Reading the Mind in the Eyes Test:" ~ ICC["2,1"] ~ .(res_print |> filter(scale == "EYES_total") |> pull(string)))) +
  scale_y_continuous(breaks = scales::breaks_pretty(n = 6))

data_reshaped_plotting |>
  filter(scale == "PTTA_total") |>
  ggplot(aes(as.factor(timepoint), score, fill = as.factor(timepoint))) +
  geom_rain(alpha = .5, rain.side = 'f1x1', id.long.var = "unique_id") +
  theme_classic() +
  scale_fill_manual(values=c("dodgerblue", "darkorange")) +
  guides(fill = 'none', color = 'none') +
  ylab("Score") +
  xlab("Time point") +
  ggtitle(bquote("Perspective Taking Task for Adults:" ~ ICC["2,1"] ~ .(res_print |> filter(scale == "PTTA_total") |> pull(string)))) +
  scale_y_continuous(breaks = scales::breaks_pretty(n = 6))

data_reshaped_plotting |>
  filter(scale == "PTP_total") |>
  ggplot(aes(as.factor(timepoint), score, fill = as.factor(timepoint))) +
  geom_rain(alpha = .5, rain.side = 'f1x1', id.long.var = "unique_id", likert = TRUE) +
  theme_classic() +
  scale_fill_manual(values=c("dodgerblue", "darkorange")) +
  guides(fill = 'none', color = 'none') +
  ylab("Score") +
  xlab("Time point") +
  ggtitle(bquote("Perspective Taking Protocol:" ~ ICC["2,1"] ~ .(res_print |> filter(scale == "PTP_total") |> pull(string)))) +
  scale_y_continuous(breaks = scales::breaks_pretty(n = 6))

```

## Internal consistency 

Cronbach's $\alpha$

```{r}

data_subset <- data_processed_after_exclusions |>
  dplyr::select(timepoint, 
                starts_with("IRI_"), 
                starts_with("EQ_"),
                starts_with("PET_"),
                starts_with("EYES_"),
                starts_with("PTP_"),
                starts_with("PTTA_")) |>
  dplyr::select(-PTP_simple, -PTP_reversed, -PTP_doublereversed) |>
  dplyr::select(-IRI_FS, -IRI_EC, -IRI_PT, -IRI_PD) |>
  dplyr::select(!ends_with("_completeness") & !ends_with("_total"))

tidy_alpha <- function(data, time, scale){
  res <- data |>
    filter(timepoint == time) |>
    dplyr::select(starts_with(scale)) |>
    psych::alpha()
  
  res2 <- res$feldt 
  
  tibble(scale = scale,
         timepoint = time,
         alpha = res2$alpha$raw_alpha,
         ci_lower = res2$lower.ci$raw_alpha,
         ci_upper = res2$upper.ci$raw_alpha)
}

res <- bind_rows(
  tidy_alpha(data = data_subset, time = 1, scale = "IRI_"),
  tidy_alpha(data = data_subset, time = 2, scale = "IRI_"),
  tidy_alpha(data = data_subset, time = 1, scale = "EQ_"),
  tidy_alpha(data = data_subset, time = 2, scale = "EQ_"),
  tidy_alpha(data = data_subset, time = 1, scale = "PET_"),
  tidy_alpha(data = data_subset, time = 2, scale = "PET_"),
  tidy_alpha(data = data_subset, time = 1, scale = "EYES_"),
  tidy_alpha(data = data_subset, time = 2, scale = "EYES_"),
  tidy_alpha(data = data_subset, time = 1, scale = "PTP_"),
  tidy_alpha(data = data_subset, time = 2, scale = "PTP_"),
  tidy_alpha(data = data_subset, time = 1, scale = "PTTA_"),
  tidy_alpha(data = data_subset, time = 2, scale = "PTTA_")
)

res |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

```

- TODO: add subscales for IRI + other scales

## Correlations

```{r}

dat <- data_processed |>
  filter(timepoint == 1)

```

### Scale correlations

```{r fig.height=4, fig.width=5}

scale_cors <- dat |>
  select(SITES, ends_with("_total")) |>
  rename_with(~ str_remove(.x, "_total")) |>
  correlation()

res <- scale_cors |>
  as.data.frame() |>
  select(Parameter1, Parameter2, r, ci_low = CI_low, ci_high = CI_high, p) 

res |>
  mutate(p = insight::format_p(p)) |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)
  
scale_cors |>
  summary() |>
  plot(show_data = "points") +
  theme_linedraw() +
  ggtitle("")

average_cors_all <- res |>
  dplyr::summarize(mean_r = mean(r)) |>
  pull(mean_r) |>
  round_half_up(digits = 2)

average_cors_ptp <- res |>
  filter(Parameter1 == "PTP" | Parameter2 == "PTP") |>
  dplyr::summarize(mean_r = mean(r)) |>
  pull(mean_r) |>
  round_half_up(digits = 2)

```

Average correlation among all scales: `r average_cors_all`

Average correlation between PTP and other scales: `r average_cors_ptp`

### Subscale correlations

```{r fig.height=8, fig.width=14}

subscale_cors <- dat |>
  select(SITES, IRI_FS, IRI_EC, IRI_PT, IRI_PD, 
         PTP_simple, PTP_reversed, PTP_doublereversed, 
         ends_with("_total")) |>
  rename_with(~ str_remove(.x, "_total")) |>
  correlation() 

subscale_cors |>
  as.data.frame() |>
  select(Parameter1, Parameter2, r, ci_low = CI_low, ci_high = CI_high, p) |>
  mutate(p = insight::format_p(p)) |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

# code repeated in order to use the rename, which screws up the table but is needed for the plot
dat |>
  select(SITES, IRI_FS, IRI_EC, IRI_PT, IRI_PD, 
         PTP_simple, PTP_reversed, PTP_doublereversed, 
         ends_with("_total")) |>
  rename_with(~ str_remove(.x, "_total")) |>
  rename_with(~ str_replace(.x, "_", "\n")) |>
  correlation()  |>
  summary() |>
  plot(show_data = "points") +
  theme_linedraw() +
  ggtitle("")

```

## SEM

```{r}

dat <- data_processed |>
  filter(timepoint == 1) |>
  select(SITES, ends_with("_total"), IRI_PT)

# model <- '
#          PT =~ SITES + IRI_total + EQ_total + PET_total + EYES_total + PTP_total + PTTA_total
#          '

model <- '
         PT =~ SITES + IRI_total + EQ_total + PET_total + EYES_total + PTP_total
         '

fit <- cfa(model = model, 
           data = dat)

fitMeasures(fit, fit.measures = c("cfi", "tli", "rmsea", "srmr", "chisq", "df", "pvalue"))

standardizedSolution(fit) |>
  filter(op != "~~") |>
  select(scale = rhs, est.std, ci.lower, ci.upper, p = pvalue) |>
  mutate(p = insight::format_p(p)) |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

```

- The overall model fits adequately, suggesting that the scales are collectively measuring a latent factor (empathy/PT). 
- Non significant loading of PTP onto the latent factor suggests it is not a good measure of this latent factor of empathy/PT.

## Rasch analysis of PTP

### Unidimensional

```{r}

# subset data
dat <- data_processed_after_exclusions |>
  filter(timepoint == 1) |>
  select(starts_with("PTP_")) |>
  select(-PTP_simple, -PTP_reversed, -PTP_doublereversed, -PTP_completeness, -PTP_total)

# fit model
#uni_model <- mirt(dat, model = 1, itemtype = "2PL")
uni_model <- mirt(dat, model = 1, itemtype = "Rasch")

# model fit stats
M2(uni_model) |>
  mutate(p = insight::format_p(p)) |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

# item parameters
coefs_uni <- coef(uni_model, IRTpars = TRUE) # Extract item parameters in IRT metric

item_parameters <- coefs_uni  |>
  discard(names(coefs_uni) == "GroupPars") %>% # Exclude GroupPars if needed
  imap_dfr(~ as_tibble(.x, rownames = "parameter") %>% 
             mutate(PTP = .y)) %>%
  relocate(PTP) |>
  rename(item = PTP) |>
  mutate(subscale = case_when(item %in% c("PTP_1", "PTP_2", "PTP_3") ~ "simple",
                              item %in% c("PTP_4", "PTP_5", "PTP_6") ~ "reversed",
                              item %in% c("PTP_7", "PTP_8", "PTP_9") ~ "doublereversed"),
         subscale = fct_relevel(subscale, "simple", "reversed", "doublereversed")) |>
  select(item, subscale, difficulty = b)

item_parameters |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

item_parameters |>
  group_by(subscale) |>
  dplyr::summarize(mean_difficulty = mean(difficulty)) |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

```

- p < 0.05 indicates potential model misfit.
- RMSEA < 0.05: Good fit; RMSEA between 0.05 and 0.08: Acceptable fit; RMSEA > 0.10: Poor fit.

### Multidimensional

```{r}

# Model specification: 'F1' loads on items 1-3, 'F2' on items 4-6, 'F3' on items 7-9.
# three_factor_model <- '
#                       F1 = 1-3
#                       F2 = 4-6
#                       F3 = 7-9
#                       '

# PTP_7 was incorrectly implemented as a single reversed trial in the survey instead of double. Corrected here.
three_factor_model <- '
                      F1 = 1-3
                      F2 = 4-7
                      F3 = 8-9
                      '

# Fit the multidimensional model
multi_model <- mirt(dat, model = three_factor_model, itemtype = "Rasch")

# Compare models using anova 
anova(uni_model, multi_model)
# > multi provides better fit

# model fit stats
M2(multi_model) |>
  mutate(p = insight::format_p(p)) |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 3))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

# item parameters
coefs_multi <- coef(multi_model, IRTpars = TRUE) # Extract item parameters in IRT metric

item_parameters_multi <- coefs_multi  |>
  discard(names(coefs_multi) == "GroupPars") %>% # Exclude GroupPars if needed
  imap_dfr(~ as_tibble(.x, rownames = "parameter") %>% 
             mutate(PTP = .y)) %>%
  relocate(PTP) |>
  rename(item = PTP) |>
  mutate(subscale = case_when(item %in% c("PTP_1", "PTP_2", "PTP_3") ~ "simple",
                              item %in% c("PTP_4", "PTP_5", "PTP_6") ~ "reversed",
                              item %in% c("PTP_7", "PTP_8", "PTP_9") ~ "doublereversed"),
         subscale = fct_relevel(subscale, "simple", "reversed", "doublereversed")) |>
  select(item, subscale, difficulty = b)

item_parameters_multi |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

item_parameters_multi |>
  group_by(subscale) |>
  dplyr::summarize(mean_difficulty = mean(difficulty)) |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

```

- p < 0.05 indicates potential model misfit.
- RMSEA < 0.05: Good fit; RMSEA between 0.05 and 0.08: Acceptable fit; RMSEA > 0.10: Poor fit.

# Session info

```{r}

sessionInfo()

```



