---
title: "Perspective taking"
subtitle: "Analyses"
author: "Ian Hussey"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

# TODO

- add distribution plots for all (sub)scales
- not all subscales in TRT plots

# Overview

All included measures are used as measures of empathy or to make conclusions about empathy. While some may be used to examine different facets of empathy, this distinction is a) not theoretically agreed upon, as there is little consensus around the structure of empathy, and therefore b) not necessarily reflected in their measurement (i.e., low correlations may represent poor convergent validity rather than good discriminant validity).

This study examines a) the reliability of these scales (internal consistency, test-retest reliability) relative to the original published estimates, and b) the risk of jingle fallacy (via correlations among [sub]scales).  

NB EQ subscales based on Lawrence et al., 2004.

```{r, include=FALSE}
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)
```

# Dependencies

```{r}

library(readr)
library(dplyr)
library(tidyr)
library(stringr)
library(forcats)
library(irr)
library(psych)
library(lavaan)
library(janitor)
library(ggplot2)
library(patchwork)
library(ggstance)
library(ggrain)
library(scales)
library(mirt)
library(metafor)
library(correlation)
library(see)
library(insight)
library(purrr)
library(knitr)
library(kableExtra)

options(scipen=999)

dir.create("plots")

```

# Load data

```{r}

data_processed <- read_csv("../data/processed/data_processed.csv") |>
  rename(PTP_sim = PTP_simple,
         PTP_rev = PTP_reversed,
         PTP_dbl = PTP_doublereversed) |>
  # display the Reading the Mind in the Eyes Test as "RMET" throughout
  rename_with(~ str_replace(.x, "^EYES", "RMET"))

data_processed_after_exclusions <- data_processed |>
  filter(exclude_master == "include")

data_sumscores <- data_processed_after_exclusions |>
  select(unique_id, timepoint, 
         SITES, 
         IRI_FS, IRI_EC, IRI_PT, IRI_PD, IRI_total,
         EQ_cog, EQ_aff, EQ_soc, EQ_total, 
         PET_total, 
         RMET_total, 
         PTP_sim, PTP_rev, PTP_dbl, PTP_total, 
         PTTA_total)

data_items <- data_processed_after_exclusions |>
  select(unique_id, 
         timepoint, 
         starts_with("IRI_"), 
         starts_with("EQ_"),
         starts_with("PET_"),
         starts_with("RMET_"),
         starts_with("PTP_"),
         starts_with("PTTA_"),
         -IRI_FS, -IRI_EC, -IRI_PT, -IRI_PD, -IRI_total,
         -EQ_cog, -EQ_aff, -EQ_soc, -EQ_total, 
         -PET_total, 
         -RMET_total, 
         -PTP_sim, -PTP_rev, -PTP_dbl, -PTP_total, 
         -PTTA_total, 
         -ends_with("_completeness"))

```

# Demographics

## Sample sizes and exclusions

```{r}

data_processed |>
  count(timepoint, exclude_master) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

```

## Analytic sample (timepoint 1)

```{r}

data_processed_after_exclusions |>
  filter(timepoint == 1) |>
  count(gender) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

data_processed_after_exclusions |>
  filter(timepoint == 1) |>
  dplyr::summarize(mean_age = mean(age),
                   sd_age = sd(age),
                   min_age = min(age),
                   max_age = max(age)) |>
  pivot_longer(cols = everything()) |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

data_processed_after_exclusions |>
  distinct(unique_id, .keep_all = TRUE) |>
  ggplot(aes(age)) +
  geom_histogram(binwidth = 5) +
  theme_linedraw()

```

# Analyses

## Test-retest

$ICC_{2,1}$

### Results

```{r}

data_reshaped <- data_sumscores |>
  pivot_wider(id_cols = unique_id,
              names_from = timepoint,
              values_from = c(SITES, 
                              IRI_FS, IRI_EC, IRI_PT, IRI_PD, IRI_total,
                              EQ_cog, EQ_aff, EQ_soc, EQ_total, 
                              PET_total, 
                              RMET_total, 
                              PTP_sim, PTP_rev, PTP_dbl, PTP_total, 
                              PTTA_total))

tidy_icc_2_1 <- function(data, scale){
  res <- data |>
    select(starts_with(scale)) |>
    irr::icc(model = "twoway", type = "agreement", unit = "single",
             r0 = 0, conf.level = 0.95)
  
  tibble(scale = scale,
         icc_2.1 = res$value,
         ci_lower = res$lbound,
         ci_upper = res$ubound)
}

res <- bind_rows(
  tidy_icc_2_1(data_reshaped, "SITES"),
  tidy_icc_2_1(data_reshaped, "IRI_FS"),
  tidy_icc_2_1(data_reshaped, "IRI_EC"),
  tidy_icc_2_1(data_reshaped, "IRI_PT"),
  tidy_icc_2_1(data_reshaped, "IRI_PD"),
  tidy_icc_2_1(data_reshaped, "IRI_total"),
  tidy_icc_2_1(data_reshaped, "EQ_total"),
  tidy_icc_2_1(data_reshaped, "EQ_cog"),
  tidy_icc_2_1(data_reshaped, "EQ_aff"),
  tidy_icc_2_1(data_reshaped, "EQ_soc"),
  tidy_icc_2_1(data_reshaped, "PET_total"),
  tidy_icc_2_1(data_reshaped, "RMET_total"),
  tidy_icc_2_1(data_reshaped, "PTP_total"),
  tidy_icc_2_1(data_reshaped, "PTP_sim"),
  tidy_icc_2_1(data_reshaped, "PTP_rev"),
  tidy_icc_2_1(data_reshaped, "PTP_dbl"),
  tidy_icc_2_1(data_reshaped, "PTTA_total")
)

# keep the ICC[2,1] estimates for later disattenuation of the correlations
icc_2_1_results <- res

res |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

```

### Plots

#### Bar

```{r fig.height=5, fig.width=6}

p_trt_scales <- res |>
  filter(str_detect(scale, "SITES") | str_detect(scale, "_total")) |>
  mutate(scale = str_remove(scale, "_total")) |>
  ggplot(aes(icc_2.1, fct_rev(scale))) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  geom_linerangeh(aes(xmin = ci_lower, xmax = ci_upper), position = position_dodge(width = .3)) +
  geom_point(position = position_dodge(width = .3)) +
  scale_x_continuous(breaks = breaks_pretty(n = 10),
                     limits = c(-.2, 1),
                     name = bquote("Test-Retest Reliability" ~ (ICC["2,1"]))) +
  theme_linedraw() +
  ylab("Scale")

p_trt_subscales <- res |>
  filter(!str_detect(scale, "_total") & !str_detect(scale, "SITES")) |>
  mutate(scale = str_replace(scale, "_", " ")) |>
  mutate(scale = str_replace(scale, "doublereversed", "double")) |>
  ggplot(aes(icc_2.1, fct_rev(scale))) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  geom_linerangeh(aes(xmin = ci_lower, xmax = ci_upper), position = position_dodge(width = .3)) +
  geom_point(position = position_dodge(width = .3)) +
  scale_x_continuous(breaks = breaks_pretty(n = 10),
                     limits = c(-.2, 1),
                     name = bquote("Test-Retest Reliability" ~ (ICC["2,1"]))) +
  theme_linedraw() +
  ylab("Subscale")

p_trt_scales + 
  p_trt_subscales + 
  plot_layout(ncol = 1, heights = c(1, 1.35))

ggsave("plots/trt.png", 
       width = 6,
       height = 5,
       dpi = 600)

```

#### Raincloud

```{r fig.height=14, fig.width=12}

round_half_up_trailing <- function(x, digits = 2) {
  x_rounded <- round_half_up(x, digits = digits)
  sprintf("%.*f", digits, x_rounded)
}

res_print <- res |>
  mutate(across(where(is.numeric), ~ round_half_up_trailing(.x, digits = 2))) |>
  mutate(string = paste0("= ", icc_2.1, ", 95% CI [", ci_lower, ", ", ci_upper, "]")) |>
  select(scale, string)

data_reshaped_plotting <- data_sumscores |>
  pivot_longer(cols = c(SITES, 
                        IRI_FS, IRI_EC, IRI_PT, IRI_PD, IRI_total,
                        EQ_cog, EQ_aff, EQ_soc, EQ_total, 
                        PET_total, 
                        RMET_total, 
                        PTP_sim, PTP_rev, PTP_dbl, PTP_total, 
                        PTTA_total),
               names_to = "scale",
               values_to = "score")


p_trt_1 <- data_reshaped_plotting |>
  filter(scale == "IRI_total") |>
  ggplot(aes(as.factor(timepoint), score, fill = as.factor(timepoint))) +
  geom_rain(alpha = .5, rain.side = 'f1x1', id.long.var = "unique_id") +
  theme_classic() +
  scale_fill_manual(values=c("dodgerblue", "darkorange")) +
  guides(fill = 'none', color = 'none') +
  ylab("Score") +
  xlab("Time point") +
  ggtitle(bquote("Interpersonal Reactivity Index:" ~ ICC["2,1"] ~ .(res_print |> filter(scale == "IRI_total") |> pull(string)))) +
  scale_y_continuous(breaks = scales::breaks_pretty(n = 6))

p_trt_2 <- data_reshaped_plotting |>
  filter(scale == "IRI_PT") |>
  ggplot(aes(as.factor(timepoint), score, fill = as.factor(timepoint))) +
  geom_rain(alpha = .5, rain.side = 'f1x1', id.long.var = "unique_id") +
  theme_classic() +
  scale_fill_manual(values=c("dodgerblue", "darkorange")) +
  guides(fill = 'none', color = 'none') +
  ylab("Score") +
  xlab("Time point") +
  ggtitle(bquote("IRI - Perspective Taking Subscale:" ~ ICC["2,1"] ~ .(res_print |> filter(scale == "IRI_PT") |> pull(string)))) +
  scale_y_continuous(breaks = scales::breaks_pretty(n = 6))

p_trt_3 <- data_reshaped_plotting |>
  filter(scale == "SITES") |>
  ggplot(aes(as.factor(timepoint), score, fill = as.factor(timepoint))) +
  geom_rain(alpha = .5, rain.side = 'f1x1', id.long.var = "unique_id", likert = TRUE) +
  theme_classic() +
  scale_fill_manual(values=c("dodgerblue", "darkorange")) +
  guides(fill = 'none', color = 'none') +
  ylab("Score") +
  xlab("Time point") +
  ggtitle(bquote("Single Item Trait Empathy Scale:" ~ ICC["2,1"] ~ .(res_print |> filter(scale == "SITES") |> pull(string)))) +
  scale_y_continuous(breaks = scales::breaks_pretty(n = 6))

p_trt_4 <- data_reshaped_plotting |>
  filter(scale == "PET_total") |>
  ggplot(aes(as.factor(timepoint), score, fill = as.factor(timepoint))) +
  geom_rain(alpha = .5, rain.side = 'f1x1', id.long.var = "unique_id") +
  theme_classic() +
  scale_fill_manual(values=c("dodgerblue", "darkorange")) +
  guides(fill = 'none', color = 'none') +
  ylab("Score") +
  xlab("Time point") +
  ggtitle(bquote("Pictoral Empathy Test:" ~ ICC["2,1"] ~ .(res_print |> filter(scale == "PET_total") |> pull(string)))) +
  scale_y_continuous(breaks = scales::breaks_pretty(n = 6))

p_trt_5 <- data_reshaped_plotting |>
  filter(scale == "EQ_total") |>
  ggplot(aes(as.factor(timepoint), score, fill = as.factor(timepoint))) +
  geom_rain(alpha = .5, rain.side = 'f1x1', id.long.var = "unique_id") +
  theme_classic() +
  scale_fill_manual(values=c("dodgerblue", "darkorange")) +
  guides(fill = 'none', color = 'none') +
  ylab("Score") +
  xlab("Time point") +
  ggtitle(bquote("Emotional Quotient:" ~ ICC["2,1"] ~ .(res_print |> filter(scale == "EQ_total") |> pull(string)))) +
  scale_y_continuous(breaks = scales::breaks_pretty(n = 6))

p_trt_6 <- data_reshaped_plotting |>
  filter(scale == "RMET_total") |>
  ggplot(aes(as.factor(timepoint), score, fill = as.factor(timepoint))) +
  geom_rain(alpha = .5, rain.side = 'f1x1', id.long.var = "unique_id") +
  theme_classic() +
  scale_fill_manual(values=c("dodgerblue", "darkorange")) +
  guides(fill = 'none', color = 'none') +
  ylab("Score") +
  xlab("Time point") +
  ggtitle(bquote("Reading the Mind in the Eyes Test:" ~ ICC["2,1"] ~ .(res_print |> filter(scale == "RMET_total") |> pull(string)))) +
  scale_y_continuous(breaks = scales::breaks_pretty(n = 6))

p_trt_7 <- data_reshaped_plotting |>
  filter(scale == "PTP_total") |>
  ggplot(aes(as.factor(timepoint), score, fill = as.factor(timepoint))) +
  geom_rain(alpha = .5, rain.side = 'f1x1', id.long.var = "unique_id", likert = TRUE) +
  theme_classic() +
  scale_fill_manual(values=c("dodgerblue", "darkorange")) +
  guides(fill = 'none', color = 'none') +
  ylab("Score") +
  xlab("Time point") +
  ggtitle(bquote("Perspective Taking Protocol:" ~ ICC["2,1"] ~ .(res_print |> filter(scale == "PTP_total") |> pull(string)))) +
  scale_y_continuous(breaks = scales::breaks_pretty(n = 6))

p_trt_8 <- data_reshaped_plotting |>
  filter(scale == "PTTA_total") |>
  ggplot(aes(as.factor(timepoint), score, fill = as.factor(timepoint))) +
  geom_rain(alpha = .5, rain.side = 'f1x1', id.long.var = "unique_id") +
  theme_classic() +
  scale_fill_manual(values=c("dodgerblue", "darkorange")) +
  guides(fill = 'none', color = 'none') +
  ylab("Score") +
  xlab("Time point") +
  ggtitle(bquote("Perspective Taking Task for Adults:" ~ ICC["2,1"] ~ .(res_print |> filter(scale == "PTTA_total") |> pull(string)))) +
  scale_y_continuous(breaks = scales::breaks_pretty(n = 6))

p_trt_1 + p_trt_2 + p_trt_3 + p_trt_4 +
  p_trt_5 + p_trt_6 + p_trt_7 + p_trt_8 +
  plot_layout(ncol = 2)

```

## Internal consistency 

Cronbach's $\alpha$

```{r}

tidy_alpha <- function(data, time, scale){
  res <- data |>
    filter(timepoint == time) |>
    dplyr::select(starts_with(scale)) |>
    psych::alpha()

  res2 <- res$feldt

  tibble(scale = scale,
         timepoint = time,
         alpha = res2$alpha$raw_alpha,
         ci_lower = res2$lower.ci$raw_alpha,
         ci_upper = res2$upper.ci$raw_alpha)
}

# variant that takes an explicit vector of items, for subscales whose items
# cannot be selected with a single starts_with() prefix
tidy_alpha_items <- function(data, time, scale, items){
  res <- data |>
    filter(timepoint == time) |>
    dplyr::select(all_of(items)) |>
    psych::alpha()

  res2 <- res$feldt

  tibble(scale = scale,
         timepoint = time,
         alpha = res2$alpha$raw_alpha,
         ci_lower = res2$lower.ci$raw_alpha,
         ci_upper = res2$upper.ci$raw_alpha)
}

# subscale item compositions (from processing.Rmd)
items_IRI_FS <- c("IRI_1", "IRI_5", "IRI_7", "IRI_12", "IRI_16", "IRI_26", "IRI_23")
items_IRI_EC <- c("IRI_2", "IRI_4", "IRI_9", "IRI_14", "IRI_18", "IRI_20", "IRI_22")
items_IRI_PT <- c("IRI_3", "IRI_8", "IRI_11", "IRI_15", "IRI_21", "IRI_25", "IRI_28")
items_IRI_PD <- c("IRI_6", "IRI_10", "IRI_13", "IRI_17", "IRI_19", "IRI_24", "IRI_27")
# EQ total is scored on 40 items; the social-skills items (EQ_30/31/33/51/53) are
# retained in the data for the EQ_soc subscale but are not part of the total score
items_EQ_total <- c("EQ_1", "EQ_4", "EQ_6", "EQ_8", "EQ_10", "EQ_11", "EQ_12", "EQ_14", "EQ_15", "EQ_18", "EQ_19", "EQ_21", "EQ_22", "EQ_25", "EQ_26", "EQ_27", "EQ_28", "EQ_29", "EQ_32", "EQ_34", "EQ_35", "EQ_36", "EQ_37", "EQ_38", "EQ_39", "EQ_41", "EQ_42", "EQ_43", "EQ_44", "EQ_46", "EQ_48", "EQ_49", "EQ_50", "EQ_52", "EQ_54", "EQ_55", "EQ_57", "EQ_58", "EQ_59", "EQ_60")
items_EQ_cog <- c("EQ_8", "EQ_19", "EQ_22", "EQ_25", "EQ_26", "EQ_35", "EQ_36", "EQ_41", "EQ_43", "EQ_44", "EQ_52", "EQ_54", "EQ_55", "EQ_58", "EQ_60")
items_EQ_aff <- c("EQ_1", "EQ_6", "EQ_18", "EQ_21", "EQ_32", "EQ_38", "EQ_39", "EQ_42", "EQ_46", "EQ_48", "EQ_50", "EQ_59")
items_EQ_soc <- c("EQ_14", "EQ_29", "EQ_30", "EQ_31", "EQ_33", "EQ_34", "EQ_51", "EQ_53")
items_PTP_sim <- c("PTP_1", "PTP_2", "PTP_3")
items_PTP_rev <- c("PTP_4", "PTP_5", "PTP_6", "PTP_7")
items_PTP_dbl <- c("PTP_8", "PTP_9")

# res <- bind_rows(
#   tidy_alpha(data = data_items, time = 1, scale = "IRI_"),
#   #tidy_alpha(data = data_items, time = 2, scale = "IRI_"),
#   tidy_alpha(data = data_items, time = 1, scale = "EQ_"),
#   #tidy_alpha(data = data_items, time = 2, scale = "EQ_"),
#   tidy_alpha(data = data_items, time = 1, scale = "PET_"),
#   #tidy_alpha(data = data_items, time = 2, scale = "PET_"),
#   tidy_alpha(data = data_items, time = 1, scale = "RMET_"),
#   #tidy_alpha(data = data_items, time = 2, scale = "RMET_")
#   tidy_alpha(data = data_items, time = 1, scale = "PTP_")
#   #tidy_alpha(data = data_items, time = 2, scale = "PTP_")
  
res <- bind_rows(
  #tidy_alpha(data = data_items, time = 1, scale = "SITES"),
  tidy_alpha(data = data_items, time = 1, scale = "IRI_"),
  tidy_alpha_items(data = data_items, time = 1, scale = "IRI_FS", items = items_IRI_FS),
  tidy_alpha_items(data = data_items, time = 1, scale = "IRI_EC", items = items_IRI_EC),
  tidy_alpha_items(data = data_items, time = 1, scale = "IRI_PT", items = items_IRI_PT),
  tidy_alpha_items(data = data_items, time = 1, scale = "IRI_PD", items = items_IRI_PD),
  tidy_alpha_items(data = data_items, time = 1, scale = "EQ_", items = items_EQ_total),
  tidy_alpha_items(data = data_items, time = 1, scale = "EQ_cog", items = items_EQ_cog),
  tidy_alpha_items(data = data_items, time = 1, scale = "EQ_aff", items = items_EQ_aff),
  tidy_alpha_items(data = data_items, time = 1, scale = "EQ_soc", items = items_EQ_soc),
  tidy_alpha(data = data_items, time = 1, scale = "PET_"),
  tidy_alpha(data = data_items, time = 1, scale = "RMET_"),
  tidy_alpha(data = data_items, time = 1, scale = "PTP_"),
  tidy_alpha_items(data = data_items, time = 1, scale = "PTP_sim", items = items_PTP_sim),
  tidy_alpha_items(data = data_items, time = 1, scale = "PTP_rev", items = items_PTP_rev),
  tidy_alpha_items(data = data_items, time = 1, scale = "PTP_dbl", items = items_PTP_dbl),
  tidy_alpha(data = data_items, time = 1, scale = "PTTA_")
)

res |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

```

### Plots

#### Bar

```{r fig.height=5, fig.width=6}

p_alpha_scales <- res |>
  filter(str_ends(scale, "_")) |>
  mutate(scale = str_remove(scale, "_")) |>
  ggplot(aes(alpha, fct_rev(scale))) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  geom_linerangeh(aes(xmin = ci_lower, xmax = ci_upper), position = position_dodge(width = .3)) +
  geom_point(position = position_dodge(width = .3)) +
  scale_x_continuous(breaks = breaks_pretty(n = 10),
                     limits = c(-.2, 1),
                     name = bquote("Internal Consistency" ~ (alpha))) +
  theme_linedraw() +
  ylab("Scale")

p_alpha_subscales <- res |>
  filter(!str_ends(scale, "_")) |>
  mutate(scale = str_replace(scale, "_", " ")) |>
  ggplot(aes(alpha, fct_rev(scale))) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  geom_linerangeh(aes(xmin = ci_lower, xmax = ci_upper), position = position_dodge(width = .3)) +
  geom_point(position = position_dodge(width = .3)) +
  scale_x_continuous(breaks = breaks_pretty(n = 10),
                     limits = c(-.2, 1),
                     name = bquote("Internal Consistency" ~ (alpha))) +
  theme_linedraw() +
  ylab("Subscale")

p_alpha_scales +
  p_alpha_subscales +
  plot_layout(ncol = 1, heights = c(1, 1.35))

ggsave("plots/internal_consistency.png",
       width = 6,
       height = 5,
       dpi = 600)

```

#### Combined

```{r fig.height=6, fig.width=7}

# harmonise (sub)scale labels across the two reliability tables: the ICC table
# names full scales "PTP_total" etc. while the alpha table names them "PTP_";
# subscale names (e.g. "PTP_sim") already match across the two
clean_label <- function(scale){
  scale |>
    str_remove("_total$") |>
    str_remove("_$") |>
    str_replace("_", " ")
}

reliability_combined <- bind_rows(
  icc_2_1_results |>
    transmute(label = clean_label(scale), estimate = icc_2.1, ci_lower, ci_upper, metric = "icc"),
  res |>  # alpha (internal consistency) results from the chunk above
    transmute(label = clean_label(scale), estimate = alpha, ci_lower, ci_upper, metric = "alpha")
) |>
  mutate(type = if_else(str_detect(label, " "), "Subscale", "Scale"),
         metric = factor(metric, levels = c("icc", "alpha")))

plot_reliability_combined <- function(data, ylab){
  ggplot(data, aes(estimate, fct_rev(label), colour = metric)) +
    geom_vline(xintercept = 0, linetype = "dotted") +
    geom_vline(xintercept = 0.70, linetype = "dashed") +
    geom_linerangeh(aes(xmin = ci_lower, xmax = ci_upper), position = position_dodgev(height = .6)) +
    geom_point(position = position_dodgev(height = .6)) +
    scale_x_continuous(breaks = breaks_pretty(n = 10),
                       limits = c(-.2, 1),
                       name = "Reliability") +
    scale_colour_manual(name = NULL,
                        values = c(icc = "dodgerblue", alpha = "darkorange"),
                        labels = c(expression("Test-Retest Reliability" ~ (ICC["2,1"])),
                                   expression("Internal Consistency" ~ (alpha)))) +
    theme_linedraw() +
    ylab(ylab)
}

plot_reliability_combined(filter(reliability_combined, type == "Scale"), "Scale") +
  plot_reliability_combined(filter(reliability_combined, type == "Subscale"), "Subscale") +
  plot_layout(ncol = 1, heights = c(1, 1.35), guides = "collect") &
  theme(legend.position = "bottom")

ggsave("plots/reliability_combined.png",
       width = 7,
       height = 6,
       dpi = 600)

```

## Correlations T1

#### Both scales and subscales

```{r fig.height=4.5}

all_cors <- data_sumscores |>
  filter(timepoint == 1) %>%
  select(-timepoint, -unique_id) %>%
  #rename_with(~ str_remove(.x, "_total")) %>%
  select(order(colnames(.))) |>
  correlation()

res <- all_cors |>
  as.data.frame() |>
  select(Parameter1, Parameter2, r, ci_low = CI_low, ci_high = CI_high, p) |>
  mutate(includes_ptp = if_else(str_detect(Parameter1, "PTP_") | str_detect(Parameter2, "PTP_"), "Correlation between PTP and other measures", "Correlation between all other measures"),
         includes_ptp = if_else(str_detect(Parameter1, "PTP_") & str_detect(Parameter2, "PTP_"), "PTP-self", includes_ptp))

res |>
  mutate(p = insight::format_p(p)) |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

p_hist_t1 <- 
  res |>
  filter(includes_ptp != "PTP-self") |>
  ggplot(aes(r)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_histogram(binwidth = 0.1, boundary = 0) +
  scale_x_continuous(limits = c(-1, 1), 
                     name = "Correlation", 
                     breaks = scales::breaks_pretty(n = 10)) + 
  scale_y_continuous(name = "Frequency", 
                     breaks = scales::breaks_pretty(n = 7)) + 
  theme_linedraw() +
  theme(panel.grid.minor.y = element_blank()) +
  facet_wrap(~ includes_ptp, ncol = 1)

#p0
  
# desired display order for the matrices: each full scale immediately above its own
# subscales, with the PTP placed first so it sits at the top-left of the matrix and
# the remaining (non-PTP) measures following in alphabetical order
measure_order <- c("PTP_total", "PTP_sim", "PTP_rev", "PTP_dbl",
                   "EQ_total", "EQ_cog", "EQ_aff", "EQ_soc",
                   "IRI_total", "IRI_FS", "IRI_EC", "IRI_PT", "IRI_PD",
                   "PET_total",
                   "PTTA_total",
                   "RMET_total",
                   "SITES")

# code repeated in order to use the rename, which screws up the table but is needed for the plot
p_mat_t1 <- data_sumscores |>
  filter(timepoint == 1) |>
  select(all_of(measure_order)) |>
  rename_with(~ str_remove(.x, "_total")) |>
  rename_with(~ str_replace(.x, "_", "\n")) |>
  correlation() %>%
  mutate(across(where(is.numeric), ~ round_half_up(., 2))) |>
  summary(redundant = TRUE) |>
  plot(show_data = "points",
       stars = FALSE) +
  theme_linedraw() +
  ggtitle("")

#p0 + coord_fixed(ratio = 1)

# scale_cors |>
#   summary() |>
#   plot(show_data = "points",
#        stars = FALSE) +
#   theme_linedraw() +
#   ggtitle("") +
#   coord_fixed(ratio = 1)

average_cors_all <- res |>
  dplyr::summarize(mean_r = mean(r),
                   sd_r = sd(r),
                   median_r = median(r),
                   mad_r = mad(r),
                   min_r = min(r),
                   max_r = max(r)) 

average_cors_all |>
  round_half_up(digits = 2) |>
  kable() |>
  kable_classic(full_width = FALSE)

```

```{r fig.height=12, fig.width=9}

p_hist_t1 + ggtitle("Correlation histogram") +
  p_mat_t1 + ggtitle("Correlation matrix") + 
  plot_layout(ncol = 1, heights = c(.4, 1))

ggsave("plots/cor_all_t1.png",
       width = 9,
       height = 12,
       dpi = 600)

```

#### Both scales and subscales - disattenuated for test-retest reliability

Each observed correlation is corrected for attenuation due to (un)reliability using the test-retest reliability (ICC[2,1]) of each measure in the pair: $r_{disattenuated} = r / \sqrt{ICC_x \cdot ICC_y}$. This estimates the correlation between the temporally stable (trait) components of the two measures.

Note that disattenuation is unstable when reliabilities are low: where a measure's test-retest reliability is near zero (notably the PTP total and subscales, ICC[2,1] <= .33), the corrected values are inflated and can exceed |1|. Such values should be read as "no reliable common signal to recover" rather than as point estimates. The table below reports the exact (unclamped) disattenuated values; the accompanying matrix plot clamps them to the valid correlation range [-1, 1] purely for display, so that the out-of-range PTP part-whole cells do not dominate the colour and point-size scales.

```{r}

# look up table of test-retest reliabilities (from the Test-retest section)
icc_lookup <- icc_2_1_results |>
  select(scale, icc = icc_2.1)

res_disattenuated <- all_cors |>
  as.data.frame() |>
  select(Parameter1, Parameter2, r) |>
  # attach the ICC[2,1] of each measure in the pair
  left_join(icc_lookup, by = c("Parameter1" = "scale")) |>
  rename(icc_1 = icc) |>
  left_join(icc_lookup, by = c("Parameter2" = "scale")) |>
  rename(icc_2 = icc) |>
  # correct for attenuation
  mutate(r_disattenuated = r / sqrt(icc_1 * icc_2))

res_disattenuated |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

```

```{r fig.height=12, fig.width=9}

# ICC[2,1] lookup keyed by the SAME renamed labels used on the plot axes,
# so it can be matched against the correlation object's Parameter1/Parameter2
icc_renamed <- icc_2_1_results |>
  mutate(scale = str_remove(scale, "_total"),
         scale = str_replace(scale, "_", "\n")) |>
  select(scale, icc = icc_2.1)

p_mat_disattenuated_t1 <- data_sumscores |>
  filter(timepoint == 1) |>
  select(all_of(measure_order)) |>
  rename_with(~ str_remove(.x, "_total")) |>
  rename_with(~ str_replace(.x, "_", "\n")) |>
  correlation() %>%
  # disattenuate each correlation by the test-retest reliabilities of the pair,
  # r_disattenuated = r / sqrt(ICC_x * ICC_y), then clamp to the valid correlation
  # range [-1, 1] for display. Exact values (which can exceed |1| where a measure's
  # reliability is low, e.g. the PTP) are reported in the table above.
  mutate(r = r / sqrt(icc_renamed$icc[match(Parameter1, icc_renamed$scale)] *
                      icc_renamed$icc[match(Parameter2, icc_renamed$scale)]),
         r = pmax(pmin(r, 1), -1)) |>
  mutate(across(where(is.numeric), ~ round_half_up(., 2))) |>
  summary(redundant = TRUE) |>
  plot(show_data = "points",
       stars = FALSE) +
  theme_linedraw() +
  ggtitle("Disattenuated for test-retest reliability")

p_mat_t1 + ggtitle("Observed correlations") +
  p_mat_disattenuated_t1 +
  plot_layout(ncol = 1)

ggsave("plots/cor_all_disattenuated_t1.png",
       width = 9,
       height = 18,
       dpi = 600)

```

#### Moderator meta-analysis: PTP vs non-PTP correlations

Each Time 1 correlation is treated as an effect size, Fisher r-to-z transformed (variance $1/(n-3)$), and entered into a mixed-effects meta-analysis with a binary moderator: whether the pair involves the PTP (or one of its subscales) with another measure, versus a correlation among two non-PTP (sub)scales. Correlations within the same instrument (a scale with its own subscales, and subscales of the same scale with one another) are part-whole / non-independent and are excluded, leaving only cross-instrument correlations. The analysis is run twice: on the observed correlations and on the correlations disattenuated for test-retest reliability.

```{r}

# strip subscale/total suffixes to identify each measure's parent instrument
strip_subscale <- function(x) str_remove(x, "_(total|FS|EC|PT|PD|cog|aff|soc|sim|rev|dbl)$")

meta_dat <- all_cors |>
  as.data.frame() |>
  select(Parameter1, Parameter2, r, n = n_Obs) |>
  left_join(icc_2_1_results |> transmute(scale, icc1 = icc_2.1), by = c("Parameter1" = "scale")) |>
  left_join(icc_2_1_results |> transmute(scale, icc2 = icc_2.1), by = c("Parameter2" = "scale")) |>
  mutate(r_disattenuated = r / sqrt(icc1 * icc2),
         # exclude within-instrument (part-whole / non-independent) correlations
         within_instrument = strip_subscale(Parameter1) == strip_subscale(Parameter2),
         # moderator: does the pair involve the PTP (or a PTP subscale)?
         moderator = if_else(str_detect(Parameter1, "^PTP") | str_detect(Parameter2, "^PTP"),
                             "PTP with other measures", "Among non-PTP measures")) |>
  filter(!within_instrument) |>
  mutate(moderator = factor(moderator, levels = c("Among non-PTP measures", "PTP with other measures")))

# Fisher r-to-z (clamp to avoid atanh(+/-1) = Inf for any over-corrected value)
fisher_z <- function(data, r_col){
  data |>
    mutate(ri = pmax(pmin(.data[[r_col]], 0.999), -0.999),
           yi = atanh(ri),
           vi = 1 / (n - 3))
}

# fit the moderator model, plus a version with cluster-robust standard errors.
# the effect sizes are dyadic (each correlation involves two measures), so they are
# not independent; we cluster on one member of each pair to get robust SEs that
# account for the shared-measure dependency
fit_meta <- function(r_col){
  dat <- fisher_z(meta_dat, r_col)
  model <- rma(yi, vi, mods = ~ moderator, data = dat)
  list(model = model,
       robust = robust(model, cluster = dat$Parameter1))
}

m_observed      <- fit_meta("r")
m_disattenuated <- fit_meta("r_disattenuated")

# number of effect sizes per group
k_by_group <- meta_dat |> count(moderator, name = "k")

# pooled estimate for each moderator group, back-transformed from Fisher z to
# Pearson's r together with its 95% CI (both model-based and cluster-robust)
preds_r <- function(fit, label){
  pm <- predict(fit$model,  newmods = c(0, 1))   # 0 = non-PTP (reference), 1 = PTP
  pr <- predict(fit$robust, newmods = c(0, 1))
  tibble(analysis = label,
         moderator = levels(meta_dat$moderator),
         r               = tanh(pm$pred),
         ci_lower        = tanh(pm$ci.lb),
         ci_upper        = tanh(pm$ci.ub),
         ci_lower_robust = tanh(pr$ci.lb),
         ci_upper_robust = tanh(pr$ci.ub))
}

bind_rows(
  preds_r(m_observed, "Observed correlations"),
  preds_r(m_disattenuated, "Disattenuated correlations")
) |>
  left_join(k_by_group, by = "moderator") |>
  mutate(across(c(r, starts_with("ci_")), ~ round_half_up(.x, digits = 2)),
         `r [95% CI]`          = paste0(r, " [", ci_lower, ", ", ci_upper, "]"),
         `r [95% CI] (robust)` = paste0(r, " [", ci_lower_robust, ", ", ci_upper_robust, "]")) |>
  select(analysis, moderator, k, `r [95% CI]`, `r [95% CI] (robust)`) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

# moderator test (difference between the two groups), with model-based and
# cluster-robust p-values (the test statistic is scale-free, so it is unchanged
# by the r-to-z transformation)
tibble(analysis = c("Observed correlations", "Disattenuated correlations"),
       `p (model)`  = c(m_observed$model$pval[2],  m_disattenuated$model$pval[2]),
       `p (robust)` = c(m_observed$robust$pval[2], m_disattenuated$robust$pval[2])) |>
  mutate(across(starts_with("p"), ~ insight::format_p(.x, stars = FALSE))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

```

All estimates are back-transformed from Fisher's z to Pearson's r for reporting: the table gives each group's pooled correlation with its 95% CI, and the moderator test (the difference between groups) is reported as a p-value, which is unchanged by the r-to-z transformation. In both analyses the correlations involving the PTP are far weaker than those among the other measures: the moderator captures essentially the whole of the (already weak) convergence in this battery. Because the effect sizes are dyadic and not fully independent (each measure appears in several pairs), we report cluster-robust 95% CIs and p-values (clustering on one member of each pair) alongside the model-based ones; the robust intervals are similar and the moderator remains highly significant in both the observed and disattenuated analyses. (The disattenuated analysis uses the observed-r sampling variance, so all of its intervals are approximate.)

##### Sensitivity analysis: excluding the RMET

The RMET itself has poor and contested psychometric properties (Higgins et al., 2023, 2024), so its inclusion could weaken the non-PTP comparison group. We therefore repeat the moderator meta-analysis after dropping every correlation that involves the RMET.

```{r}

meta_dat_sens <- meta_dat |>
  filter(Parameter1 != "RMET_total", Parameter2 != "RMET_total")

fit_sens <- function(r_col){
  dat   <- fisher_z(meta_dat_sens, r_col)
  model <- rma(yi, vi, mods = ~ moderator, data = dat)
  list(model = model, robust = robust(model, cluster = dat$Parameter1))
}

s_observed      <- fit_sens("r")
s_disattenuated <- fit_sens("r_disattenuated")

k_by_group_sens <- meta_dat_sens |> count(moderator, name = "k")

bind_rows(
  preds_r(s_observed, "Observed correlations"),
  preds_r(s_disattenuated, "Disattenuated correlations")
) |>
  left_join(k_by_group_sens, by = "moderator") |>
  mutate(across(c(r, starts_with("ci_")), ~ round_half_up(.x, digits = 2)),
         `r [95% CI]`          = paste0(r, " [", ci_lower, ", ", ci_upper, "]"),
         `r [95% CI] (robust)` = paste0(r, " [", ci_lower_robust, ", ", ci_upper_robust, "]")) |>
  select(analysis, moderator, k, `r [95% CI]`, `r [95% CI] (robust)`) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

tibble(analysis = c("Observed correlations", "Disattenuated correlations"),
       `p (model)`  = c(s_observed$model$pval[2],  s_disattenuated$model$pval[2]),
       `p (robust)` = c(s_observed$robust$pval[2], s_disattenuated$robust$pval[2])) |>
  mutate(across(starts_with("p"), ~ insight::format_p(.x, stars = FALSE))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

```

Excluding the RMET, if anything, sharpens the contrast: the non-PTP measures cohere slightly more once the RMET is removed (*r* = .31 observed, .39 disattenuated), the PTP is unchanged (*r* ≈ .01–.03), and the moderator remains highly significant.

<!-- #### Scale correlations -->

<!-- ```{r fig.height=4.5} -->

<!-- scale_cors <- dat |> -->
<!--   select(SITES, ends_with("_total")) |> -->
<!--   rename_with(~ str_remove(.x, "_total")) %>% -->
<!--   select(order(colnames(.))) |> -->
<!--   correlation() -->

<!-- res <- scale_cors |> -->
<!--   as.data.frame() |> -->
<!--   select(Parameter1, Parameter2, r, ci_low = CI_low, ci_high = CI_high, p)  -->

<!-- res |> -->
<!--   mutate(p = insight::format_p(p)) |> -->
<!--   mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |> -->
<!--   kable(align = "r") |> -->
<!--   kable_classic(full_width = FALSE) -->

<!-- p1_t1 <-  -->
<!--   ggplot(res, aes(r)) + -->
<!--   geom_vline(xintercept = 0, linetype = "dashed") + -->
<!--   geom_histogram(binwidth = 0.1, boundary = 0) + -->
<!--   scale_x_continuous(limits = c(-1, 1),  -->
<!--                      name = "Correlation",  -->
<!--                      breaks = scales::breaks_pretty(n = 10)) +  -->
<!--   scale_y_continuous(name = "Frequency",  -->
<!--                      breaks = scales::breaks_pretty(n = 7)) +  -->
<!--   theme_linedraw() + -->
<!--   theme(panel.grid.minor.y = element_blank()) -->

<!-- #p1 -->

<!-- p2_t1 <-  -->
<!--   scale_cors |> -->
<!--   summary(redundant = TRUE) |> -->
<!--   plot(show_data = "points", -->
<!--        stars = FALSE) + -->
<!--   theme_linedraw() + -->
<!--   ggtitle("") -->

<!-- #p2 + coord_fixed(ratio = 1) -->

<!-- # scale_cors |> -->
<!-- #   summary() |> -->
<!-- #   plot(show_data = "points", -->
<!-- #        stars = FALSE) + -->
<!-- #   theme_linedraw() + -->
<!-- #   ggtitle("") + -->
<!-- #   coord_fixed(ratio = 1) -->

<!-- average_cors_all <- res |> -->
<!--   dplyr::summarize(mean_r = mean(r), -->
<!--                    sd_r = sd(r), -->
<!--                    median_r = median(r), -->
<!--                    mad_r = mad(r), -->
<!--                    min_r = min(r), -->
<!--                    max_r = max(r))  -->

<!-- average_cors_all |> -->
<!--   round_half_up(digits = 2) |> -->
<!--   kable() |> -->
<!--   kable_classic(full_width = FALSE) -->

<!-- ``` -->

<!-- ```{r fig.height=7, fig.width=6} -->

<!-- p1_t1 + ggtitle("Correlation histogram") + -->
<!--   p2_t1 + ggtitle("Correlation matrix") +  -->
<!--   plot_layout(ncol = 1, heights = c(.4, 1)) -->

<!-- ggsave("plots/cor_scales_t1.png",  -->
<!--        width = 6, -->
<!--        height = 7, -->
<!--        dpi = 600) -->

<!-- ``` -->

<!-- #### Subscale correlations -->

<!-- ```{r fig.height=6, fig.width=11} -->

<!-- subscale_cors <- dat |> -->
<!--   select(SITES,  -->
<!--          IRI_FS, IRI_EC, IRI_PT, IRI_PD,  -->
<!--          EQ_cog, EQ_aff, EQ_soc,  -->
<!--          PET_total, -->
<!--          PTP_sim, PTP_rev, PTP_dbl) |> -->
<!--   rename_with(~ str_remove(.x, "_total")) |> -->
<!--   correlation()  -->

<!-- subscale_cors |> -->
<!--   as.data.frame() |> -->
<!--   select(Parameter1, Parameter2, r, ci_low = CI_low, ci_high = CI_high, p) |> -->
<!--   mutate(p = insight::format_p(p)) |> -->
<!--   mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |> -->
<!--   kable(align = "r") |> -->
<!--   kable_classic(full_width = FALSE) -->

<!-- p3_t1 <-  -->
<!--   ggplot(subscale_cors, aes(r)) + -->
<!--   geom_vline(xintercept = 0, linetype = "dashed") + -->
<!--   geom_histogram(binwidth = 0.1, boundary = 0) + -->
<!--   scale_x_continuous(limits = c(-1, 1),  -->
<!--                      name = "Correlation",  -->
<!--                      breaks = scales::breaks_pretty(n = 10)) +  -->
<!--   scale_y_continuous(name = "Frequency",  -->
<!--                      breaks = scales::breaks_pretty(n = 7)) +  -->
<!--   theme_linedraw() + -->
<!--   theme(panel.grid.minor.y = element_blank()) -->

<!-- #p3_t1 -->

<!-- # code repeated in order to use the rename, which screws up the table but is needed for the plot -->
<!-- p4_t1 <- dat |> -->
<!--   select(SITES,  -->
<!--          IRI_FS, IRI_EC, IRI_PT, IRI_PD,  -->
<!--          EQ_cog, EQ_aff, EQ_soc,  -->
<!--          PET_total, -->
<!--          PTP_sim, PTP_rev, PTP_dbl) |> -->
<!--   rename_with(~ str_remove(.x, "_total")) |> -->
<!--   rename_with(~ str_replace(.x, "_", "\n")) %>% -->
<!--   select(order(colnames(.))) |> -->
<!--   correlation() %>% -->
<!--   mutate(across(where(is.numeric), ~ round_half_up(., 2))) |> -->
<!--   summary(redundant = TRUE) |> -->
<!--   plot(show_data = "points", -->
<!--        stars = FALSE) + -->
<!--   theme_linedraw() + -->
<!--   ggtitle("") -->

<!-- #p4_t1 -->

<!-- ``` -->

<!-- ```{r fig.height=9, fig.width=7} -->

<!-- p3_t1 + ggtitle("Correlation histogram") + -->
<!--   p4_t1 + ggtitle("Correlation matrix") +  -->
<!--   plot_layout(ncol = 1, heights = c(.4, 1)) -->

<!-- ggsave("plots/cor_subscales_t1.png", -->
<!--        width = 7, -->
<!--        height = 9, -->
<!--        dpi = 600) -->

<!-- ``` -->

#### Perspective taking (sub)scale correlations

Subset of the (sub)scales that specifically target perspective taking: the IRI Perspective Taking subscale (IRI_PT), the EQ Cognitive empathy subscale (EQ_cog), the Reading the Mind in the Eyes Test (RMET), the Perspective Taking Protocol subscales (PTP_sim/rev/dbl), and the Perspective Taking Task for Adults (PTTA).

```{r fig.height=6, fig.width=11}

pt_cors <- data_sumscores |>
  filter(timepoint == 1) |>
  select(IRI_PT,
         EQ_cog,
         RMET_total,
         PTP_sim, PTP_rev, PTP_dbl,
         PTTA_total) |>
  rename_with(~ str_remove(.x, "_total")) |>
  correlation()

pt_cors |>
  as.data.frame() |>
  select(Parameter1, Parameter2, r, ci_low = CI_low, ci_high = CI_high, p) |>
  mutate(p = insight::format_p(p)) |>
  mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |>
  kable(align = "r") |>
  kable_classic(full_width = FALSE)

p5_t1 <-
  ggplot(pt_cors, aes(r)) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_histogram(binwidth = 0.1, boundary = 0) +
  scale_x_continuous(limits = c(-1, 1),
                     name = "Correlation",
                     breaks = scales::breaks_pretty(n = 10)) +
  scale_y_continuous(name = "Frequency",
                     breaks = scales::breaks_pretty(n = 7)) +
  theme_linedraw() +
  theme(panel.grid.minor.y = element_blank())

#p5_t1

# code repeated in order to use the rename, which screws up the table but is needed for the plot
p6_t1 <- data_sumscores |>
  filter(timepoint == 1) |>
  # PTP first so it sits at the top-left of the matrix; other measures alphabetical
  select(PTP_sim, PTP_rev, PTP_dbl,
         EQ_cog,
         IRI_PT,
         PTTA_total,
         RMET_total) |>
  rename_with(~ str_remove(.x, "_total")) |>
  rename_with(~ str_replace(.x, "_", "\n")) |>
  correlation() %>%
  mutate(across(where(is.numeric), ~ round_half_up(., 2))) |>
  summary(redundant = TRUE) |>
  plot(show_data = "points",
       stars = FALSE) +
  theme_linedraw() +
  ggtitle("")

#p6_t1

```

```{r fig.height=9, fig.width=7}

p6_t1 + ggtitle("Correlation matrix") 

ggsave("plots/cor_pt_t1.png",
       width = 7,
       height = 7,
       dpi = 600)

```

<!-- ### T2 -->

<!-- ```{r} -->

<!-- dat <- data_processed |> -->
<!--   filter(timepoint == 2) -->

<!-- ``` -->

<!-- #### Scale correlations -->

<!-- ```{r fig.height=4.5} -->

<!-- scale_cors <- dat |> -->
<!--   select(SITES, ends_with("_total")) |> -->
<!--   rename_with(~ str_remove(.x, "_total")) %>% -->
<!--   select(order(colnames(.))) |> -->
<!--   correlation() -->

<!-- res <- scale_cors |> -->
<!--   as.data.frame() |> -->
<!--   select(Parameter1, Parameter2, r, ci_low = CI_low, ci_high = CI_high, p)  -->

<!-- res |> -->
<!--   mutate(p = insight::format_p(p)) |> -->
<!--   mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |> -->
<!--   kable(align = "r") |> -->
<!--   kable_classic(full_width = FALSE) -->

<!-- p1_t2 <-  -->
<!--   ggplot(res, aes(r)) + -->
<!--   geom_vline(xintercept = 0, linetype = "dashed") + -->
<!--   geom_histogram(binwidth = 0.1, boundary = 0) + -->
<!--   scale_x_continuous(limits = c(-1, 1),  -->
<!--                      name = "Correlation",  -->
<!--                      breaks = scales::breaks_pretty(n = 10)) +  -->
<!--   scale_y_continuous(name = "Frequency",  -->
<!--                      breaks = scales::breaks_pretty(n = 7)) +  -->
<!--   theme_linedraw() + -->
<!--   theme(panel.grid.minor.y = element_blank()) -->

<!-- #p1_t2 -->

<!-- p2_t2 <-  -->
<!--   scale_cors |> -->
<!--   summary(redundant = TRUE) |> -->
<!--   plot(show_data = "points", -->
<!--        stars = FALSE) + -->
<!--   theme_linedraw() + -->
<!--   ggtitle("") -->

<!-- #p2_t2 + coord_fixed(ratio = 1) -->

<!-- # scale_cors |> -->
<!-- #   summary() |> -->
<!-- #   plot(show_data = "points", -->
<!-- #        stars = FALSE) + -->
<!-- #   theme_linedraw() + -->
<!-- #   ggtitle("") + -->
<!-- #   coord_fixed(ratio = 1) -->

<!-- average_cors_all <- res |> -->
<!--   dplyr::summarize(mean_r = mean(r), -->
<!--                    sd_r = sd(r), -->
<!--                    median_r = median(r), -->
<!--                    mad_r = mad(r), -->
<!--                    min_r = min(r), -->
<!--                    max_r = max(r))  -->

<!-- average_cors_all |> -->
<!--   round_half_up(digits = 2) |> -->
<!--   kable() |> -->
<!--   kable_classic(full_width = FALSE) -->

<!-- ``` -->

<!-- ```{r fig.height=7, fig.width=6} -->

<!-- p1_t2 + ggtitle("Correlation histogram") + -->
<!--   p2_t2 + ggtitle("Correlation matrix") +  -->
<!--   plot_layout(ncol = 1, heights = c(.4, 1)) -->

<!-- ggsave("plots/cor_scales_t2.png",  -->
<!--        width = 6, -->
<!--        height = 7, -->
<!--        dpi = 600) -->

<!-- ``` -->

<!-- #### Subscale correlations -->

<!-- ```{r fig.height=6, fig.width=11} -->

<!-- subscale_cors <- dat |> -->
<!--   select(SITES,  -->
<!--          IRI_FS, IRI_EC, IRI_PT, IRI_PD,  -->
<!--          EQ_cog, EQ_aff, EQ_soc,  -->
<!--          PET_total, -->
<!--          RMET_total) |> -->
<!--   rename_with(~ str_remove(.x, "_total")) |> -->
<!--   correlation()  -->

<!-- subscale_cors |> -->
<!--   as.data.frame() |> -->
<!--   select(Parameter1, Parameter2, r, ci_low = CI_low, ci_high = CI_high, p) |> -->
<!--   mutate(p = insight::format_p(p)) |> -->
<!--   mutate(across(where(is.numeric), ~ round_half_up(.x, digits = 2))) |> -->
<!--   kable(align = "r") |> -->
<!--   kable_classic(full_width = FALSE) -->

<!-- p3_t2 <-  -->
<!--   ggplot(subscale_cors, aes(r)) + -->
<!--   geom_vline(xintercept = 0, linetype = "dashed") + -->
<!--   geom_histogram(binwidth = 0.1, boundary = 0) + -->
<!--   scale_x_continuous(limits = c(-1, 1),  -->
<!--                      name = "Correlation",  -->
<!--                      breaks = scales::breaks_pretty(n = 10)) +  -->
<!--   scale_y_continuous(name = "Frequency",  -->
<!--                      breaks = scales::breaks_pretty(n = 7)) +  -->
<!--   theme_linedraw() + -->
<!--   theme(panel.grid.minor.y = element_blank()) -->

<!-- #p3_t2 -->

<!-- # code repeated in order to use the rename, which screws up the table but is needed for the plot -->
<!-- p4_t2 <- dat |> -->
<!--   select(SITES,  -->
<!--          IRI_FS, IRI_EC, IRI_PT, IRI_PD,  -->
<!--          EQ_cog, EQ_aff, EQ_soc,  -->
<!--          PET_total, -->
<!--          RMET_total) |> -->
<!--   rename_with(~ str_remove(.x, "_total")) |> -->
<!--   rename_with(~ str_replace(.x, "_", "\n")) %>% -->
<!--   select(order(colnames(.))) |> -->
<!--   correlation() %>% -->
<!--   mutate(across(where(is.numeric), ~ round_half_up(., 2))) |> -->
<!--   summary(redundant = TRUE) |> -->
<!--   plot(show_data = "points", -->
<!--        stars = FALSE) + -->
<!--   theme_linedraw() + -->
<!--   ggtitle("") -->

<!-- #p4_t2 -->

<!-- ``` -->

<!-- ```{r fig.height=9, fig.width=7} -->

<!-- p3_t2 + ggtitle("Correlation histogram") + -->
<!--   p4_t2 + ggtitle("Correlation matrix") +  -->
<!--   plot_layout(ncol = 1, heights = c(.4, 1)) -->

<!-- ggsave("plots/cor_subscales_t2.png",  -->
<!--        width = 7, -->
<!--        height = 9, -->
<!--        dpi = 600) -->

<!-- ``` -->

<!-- ### Both times - scales -->

<!-- ```{r fig.height=6, fig.width=9.35} -->

<!-- p1_t1 + ggtitle("Correlation histogram (T1)") + -->
<!--   p1_t2 + ggtitle("Correlation matrix (T2)") +  -->
<!--   p2_t1 + ggtitle("Correlation histogram (T1)") + -->
<!--   p2_t2 + ggtitle("Correlation matrix (T2)") +  -->
<!--   plot_layout(ncol = 2, heights = c(.4, 1), guides = "collect") -->

<!-- ggsave("plots/cor_scales_both.png",  -->
<!--        width = 9.35, -->
<!--        height = 6, -->
<!--        dpi = 600) -->

<!-- ``` -->

<!-- ### Both times - subscales -->

<!-- ```{r fig.height=9, fig.width=13.2} -->

<!-- p3_t1 + ggtitle("Correlation histogram (T1)") + -->
<!--   p3_t2 + ggtitle("Correlation matrix (T2)") +  -->
<!--   p4_t1 + ggtitle("Correlation histogram (T1)") + -->
<!--   p4_t2 + ggtitle("Correlation matrix (T2)") +  -->
<!--   plot_layout(ncol = 2, heights = c(.4, 1), guides = "collect") -->

<!-- ggsave("plots/cor_subscales_both.png",  -->
<!--        width = 13.2, -->
<!--        height = 9, -->
<!--        dpi = 600) -->

<!-- ``` -->


# Session info

```{r}

sessionInfo()

```



